Supplementary For\\ MGRFE: multilayer recursive feature elimination based on an embedded genetic algorithm for cancer classification

### 2019-06-23 MGRFE-TCBB-2019-06-03/supplementary.tex
Keep Calm and Carry On.

	\begin{algorithm}
		\SetKwInOut{Input}{Input}
		\SetKwInOut{Output}{Output}
		\Input{A microarray gene expression data}
		\Output{The optimal gene feature combination for phenotype classification}
		\SetAlgorithmName{Pseudocode}
		\text{}
		The \textit{t}-test-based gene ranking to generate the candidate gene set $G$\;
		The MIC-based gene ranking to narrow $G$\;
		Set $GC$, the list of optimal gene combinations in MGRFE, to empty\;
		\While{the maximal iterative layer number not reached}
		{
			Initialize and run a layer of GA-RFE (Pseudocode 2) based on $G$\;
			\For{each GA-RFE}
			{
				Add the returned optimal gene combinations to $GC$\;
			}
			Sort the optimal gene combinations in $GC$ and only preserve the top ranked ones\;
			Use the genes in the top ranked gene combinations in $GC$ to form a reduced $G$;
		}
		Multiple k-fold CV on the gene combinations in $GC$\;
		Return the final selected gene combination\;
		\caption{MGRFE: multilayer iterative feature selection using GA-RFE}\label{Algo:MGRFE}
	\end{algorithm}

@@

	\begin{algorithm}
		\SetKwInOut{Input}{Input}
		\SetKwInOut{Output}{Output}
		\SetAlgorithmName{Pseudocode}
		\text{}
		\Input{GA population $P$, Maximal evolution times $T$}
		\Output{Updated $P$, The optimal gene feature combinations in GA}
		Set $GC$, the list of optimal gene combinations in GA, to empty\;
		\While{the maximal evolution times $T$ not reached}
		{
			Perform mutation operator\;
			Perform crossover operator\;
			Fitness calculation of each GA individual by k-fold CV\;
			Truncation selection to form the updated $P$\;
		}
		Sort the GA individuals in $P$ and select the top ones to form $GC$\;
		Return the updated population $P$ and the optimal gene combinations in $GC$\;
		\caption{Embedded GA}\label{Algo:GA}
	\end{algorithm}

>>>>

	\begin{algorithm}
		\SetKwInOut{Input}{Input}
		\SetKwInOut{Output}{Output}
		\Input{A microarray gene expression data}
		\Output{The optimal gene feature combination for phenotype classification}
		\SetAlgorithmName{Pseudocode}
		\text{}
		The \textit{t}-test-based gene ranking to generate the candidate gene set $G$\;
		The MIC-based gene ranking to narrow $G$\;
		Set $GC$, the list of optimal gene combinations in MGRFE, to empty\;
		\While{the maximal iterative layer number not reached}
		{
			Initialize and run a layer of GA-RFE (Pseudocode 2) based on $G$\;
			\For{each GA-RFE}
			{
				Add the returned optimal gene combinations to $GC$\;
			}
			Sort the optimal gene combinations in $GC$ and only preserve the top ranked ones\;
			Use the genes in the top ranked gene combinations in $GC$ to form a reduced $G$;
		}
		Multiple \textit{k}-fold CV on the gene combinations in $GC$\;
		Return the final selected gene combination\;
		\caption{MGRFE: multilayer iterative feature selection using GA-RFE}\label{Algo:MGRFE}
	\end{algorithm}

@@

	\begin{algorithm}
		\SetKwInOut{Input}{Input}
		\SetKwInOut{Output}{Output}
		\SetAlgorithmName{Pseudocode}
		\text{}
		\Input{GA population $P$, Maximal evolution times $T$}
		\Output{Updated $P$, The optimal gene feature combinations in GA}
		Set $GC$, the list of optimal gene combinations in GA, to empty\;
		\While{the maximal evolution times $T$ not reached}
		{
			Perform mutation operator\;
			Perform crossover operator\;
			Fitness calculation of each GA individual by \textit{k}-fold CV\;
			Truncation selection to form the updated $P$\;
		}
		Sort the GA individuals in $P$ and select the top ones to form $GC$\;
		Return the updated population $P$ and the optimal gene combinations in $GC$\;
		\caption{Embedded GA}\label{Algo:GA}
	\end{algorithm}
